Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-10-27 manuscript/supporting_information.Rmd
updates corrections to manuscript and si

**Stan code for model**
```{r rec_stan, echo=TRUE, eval=FALSE}
data{
  int<lower=0> N; // observations
  int<lower=0> Yrs; // years
  int<lower=0> yid[N]; // year id
  int<lower=0> Covs; // climate covariates
  int<lower=0> G; // groups
  int<lower=0> gid[N]; // group id
  int<lower=0> Y[N]; // observation vector
  matrix[N,Covs] C; // climate matrix
  vector[N] parents1; // crowding vector
  vector[N] parents2; // crowding vector
  real<lower=0> tau; // prior variance
}
parameters{
  real a_mu;
  vector[Yrs] a;
  vector[Covs] b2;
  real dd;
  real gint[G];
  real<lower=0> sig_a;
  real<lower=0> theta;
  real<lower=0> sig_G;
  real<lower=0, upper=1> u;
}
transformed parameters{
real mu[N];
vector[N] climEff;
vector[N] trueP1;
vector[N] trueP2;
vector[N] lambda;
vector[N] q;
climEff <- C*b2;
  for(n in 1:N){
    trueP1[n] <- parents1[n]*u + parents2[n]*(1-u);
    trueP2[n] <- sqrt(trueP1[n]);
    mu[n] <- exp(a[yid[n]] + gint[gid[n]] + dd*trueP2[n] + climEff[n]);
    lambda[n] <- trueP1[n]*mu[n];
    q[n] <- lambda[n]*theta;
  }
}
model{
// Priors
  u ~ uniform(0,1);
  theta ~ uniform(0,10);
  a_mu ~ normal(0,10);
  dd ~ uniform(-10,10);
  sig_a ~ cauchy(0,5);
  sig_G ~ cauchy(0,5);
  for(g in 1:G)
   gint[g] ~ normal(0, sig_G);
  for(y in 1:Yrs){
    a[y] ~ normal(a_mu, sig_a);
  }
  for(j in 1:Covs)
    b2[j] ~ normal(0, tau);

// Likelihood
  Y ~ neg_binomial_2(q, theta);
}

@@

@@

\begin{table}[ht]
\centering
\caption {Statistical tests to assess whether models without climate covariates have higher accuracy and lower error than models with climate covariates. t-tests are one-sided.}
\begin{footnotesize}
\begin{tabular}{lllrrrl}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species \\ 
  \hline
simple IPM vs. climate IPM & rho & t & -1.703 & 279.000 & 0.955 & BOGR \\ 
  simple IPM vs. climate IPM & MAE & t & -3.715 & 280.000 & 1.000 & BOGR \\ 
  simple QBM vs. climate QBM & rho & t & -1.798 & 279.000 & 0.963 & BOGR \\ 
  simple QBM vs. climate QBM & MAE & t & -3.340 & 280.000 & 1.000 & BOGR \\ 
  simple IPM vs. climate IPM & rho & t & 0.246 & 169.000 & 0.403 & HECO \\ 
  simple IPM vs. climate IPM & MAE & t & -1.472 & 170.000 & 0.929 & HECO \\ 
  simple QBM vs. climate QBM & rho & t & 0.747 & 169.000 & 0.228 & HECO \\ 
  simple QBM vs. climate QBM & MAE & t & 1.145 & 170.000 & 0.127 & HECO \\ 
  simple IPM vs. climate IPM & rho & t & 0.201 & 215.000 & 0.421 & PASM \\ 
  simple IPM vs. climate IPM & MAE & t & -0.592 & 216.000 & 0.723 & PASM \\ 
  simple QBM vs. climate QBM & rho & t & 0.631 & 215.000 & 0.264 & PASM \\ 
  simple QBM vs. climate QBM & MAE & t & 4.276 & 216.000 & 0.000 & PASM \\ 
  simple IPM vs. climate IPM & rho & t & -1.072 & 195.000 & 0.858 & POSE \\ 
  simple IPM vs. climate IPM & MAE & t & -1.911 & 196.000 & 0.971 & POSE \\ 
  simple QBM vs. climate QBM & rho & t & -1.564 & 195.000 & 0.940 & POSE \\ 
  simple QBM vs. climate QBM & MAE & t & -2.468 & 196.000 & 0.993 & POSE \\ 
   \hline
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{table}[ht]
\centering
\caption {Statistical tests of model comparisons. Table shows results from one-sided t-tests for the particular comparison.}
\begin{footnotesize}
\begin{tabular}{lllrrrl}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species \\ 
  \hline
climate IPM vs. simple IPM & rho & t & 0.798 & 279.000 & 0.213 & BOGR \\ 
  climate IPM vs. simple IPM & MAE & t & 1.347 & 280.000 & 0.910 & BOGR \\ 
  climate QBM vs. simple QBM & rho & t & 0.526 & 279.000 & 0.300 & BOGR \\ 
  climate QBM vs. simple QBM & MAE & t & -0.478 & 280.000 & 0.317 & BOGR \\ 
  simple IPM vs. simple QBM & rho & t & -0.961 & 279.000 & 0.831 & BOGR \\ 
  simple IPM vs. simple QBM & MAE & t & 0.088 & 280.000 & 0.535 & BOGR \\ 
  climate IPM vs. climate QBM & rho & t & -0.024 & 279.000 & 0.509 & BOGR \\ 
  climate IPM vs. climate QBM & MAE & t & 2.289 & 280.000 & 0.989 & BOGR \\ 
  climate IPM vs. simple IPM & rho & t & 0.455 & 169.000 & 0.325 & HECO \\ 
  climate IPM vs. simple IPM & MAE & t & -2.292 & 170.000 & 0.012 & HECO \\ 
  climate QBM vs. simple QBM & rho & t & 0.051 & 169.000 & 0.480 & HECO \\ 
  climate QBM vs. simple QBM & MAE & t & -0.746 & 170.000 & 0.228 & HECO \\ 
  simple IPM vs. simple QBM & rho & t & -0.461 & 169.000 & 0.677 & HECO \\ 
  simple IPM vs. simple QBM & MAE & t & 1.626 & 170.000 & 0.947 & HECO \\ 
  climate IPM vs. climate QBM & rho & t & -0.299 & 169.000 & 0.617 & HECO \\ 
  climate IPM vs. climate QBM & MAE & t & 0.289 & 170.000 & 0.613 & HECO \\ 
  climate IPM vs. simple IPM & rho & t & -0.883 & 215.000 & 0.811 & PASM \\ 
  climate IPM vs. simple IPM & MAE & t & 0.410 & 216.000 & 0.659 & PASM \\ 
  climate QBM vs. simple QBM & rho & t & -0.008 & 215.000 & 0.503 & PASM \\ 
  climate QBM vs. simple QBM & MAE & t & 3.218 & 216.000 & 0.999 & PASM \\ 
  simple IPM vs. simple QBM & rho & t & 0.363 & 215.000 & 0.359 & PASM \\ 
  simple IPM vs. simple QBM & MAE & t & -0.276 & 216.000 & 0.391 & PASM \\ 
  climate IPM vs. climate QBM & rho & t & 0.600 & 215.000 & 0.274 & PASM \\ 
  climate IPM vs. climate QBM & MAE & t & -3.487 & 216.000 & 0.000 & PASM \\ 
  climate IPM vs. simple IPM & rho & t & 1.538 & 195.000 & 0.063 & POSE \\ 
  climate IPM vs. simple IPM & MAE & t & -1.844 & 196.000 & 0.033 & POSE \\ 
  climate QBM vs. simple QBM & rho & t & 1.616 & 195.000 & 0.054 & POSE \\ 
  climate QBM vs. simple QBM & MAE & t & -0.963 & 196.000 & 0.168 & POSE \\ 
  simple IPM vs. simple QBM & rho & t & 1.075 & 195.000 & 0.142 & POSE \\ 
  simple IPM vs. simple QBM & MAE & t & -0.788 & 196.000 & 0.216 & POSE \\ 
  climate IPM vs. climate QBM & rho & t & 1.721 & 195.000 & 0.043 & POSE \\ 
  climate IPM vs. climate QBM & MAE & t & -1.830 & 196.000 & 0.034 & POSE \\ 
   \hline
\end{tabular}
\end{footnotesize}
\end{table}

>>>>

**Stan code for model**
```{r rec_stan, echo=TRUE, eval=FALSE}
data{
  int<lower=0> N; // observations
  int<lower=0> Yrs; // years
  int<lower=0> yid[N]; // year id
  int<lower=0> Covs; // climate covariates
  int<lower=0> G; // groups
  int<lower=0> gid[N]; // group id
  int<lower=0> Y[N]; // observation vector
  matrix[N,Covs] C; // climate matrix
  vector[N] parents1; // crowding vector
  vector[N] parents2; // crowding vector
  real<lower=0> tau; // prior variance
}
parameters{
  real a_mu;
  vector[Yrs] a;
  vector[Covs] b2;
  real dd;
  real gint[G];
  real<lower=0> sig_a;
  real<lower=0> theta;
  real<lower=0> sig_G;
  real<lower=0, upper=1> u;
}
transformed parameters{
real mu[N];
vector[N] climEff;
vector[N] trueP1;
vector[N] trueP2;
vector[N] lambda;
climEff <- C*b2;
  for(n in 1:N){
    trueP1[n] <- parents1[n]*u + parents2[n]*(1-u);
    trueP2[n] <- sqrt(trueP1[n]);
    mu[n] <- exp(a[yid[n]] + gint[gid[n]] + dd*trueP2[n] + climEff[n]);
    lambda[n] <- trueP1[n]*mu[n];
  }
}
model{
// Priors
  u ~ uniform(0,1);
  theta ~ uniform(0,10);
  a_mu ~ normal(0,10);
  dd ~ uniform(-10,10);
  sig_a ~ cauchy(0,5);
  sig_G ~ cauchy(0,5);
  for(g in 1:G)
   gint[g] ~ normal(0, sig_G);
  for(y in 1:Yrs){
    a[y] ~ normal(a_mu, sig_a);
  }
  for(j in 1:Covs)
    b2[j] ~ normal(0, tau);

// Likelihood
  Y ~ neg_binomial_2(lambda, theta);
}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=6in]{./components/forecast_accuracy_means_mockup.png}
  \caption{Comparison of one-step-ahead, out-of-sample forecast accuracy (mean correlation between observations and predictions) between the IPM and QBM models with and without the inclusion of climate covariates.}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption {Statistical tests to assess whether models without climate covariates have higher accuracy and lower error than models with climate covariates. t-tests are one-sided.}
\begin{footnotesize}
\begin{tabular}{lllrrrl}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species \\ 
  \hline
simple IPM vs. climate IPM & rho & t & -1.196 & 279.000 & 0.884 & BOGR \\ 
  simple IPM vs. climate IPM & MAE & t & -2.333 & 280.000 & 0.990 & BOGR \\ 
  simple QBM vs. climate QBM & rho & t & -1.798 & 279.000 & 0.963 & BOGR \\ 
  simple QBM vs. climate QBM & MAE & t & -3.340 & 280.000 & 1.000 & BOGR \\ 
  simple IPM vs. climate IPM & rho & t & -0.037 & 169.000 & 0.515 & HECO \\ 
  simple IPM vs. climate IPM & MAE & t & -2.130 & 170.000 & 0.983 & HECO \\ 
  simple QBM vs. climate QBM & rho & t & 0.747 & 169.000 & 0.228 & HECO \\ 
  simple QBM vs. climate QBM & MAE & t & 1.145 & 170.000 & 0.127 & HECO \\ 
  simple IPM vs. climate IPM & rho & t & 0.097 & 215.000 & 0.462 & PASM \\ 
  simple IPM vs. climate IPM & MAE & t & -0.556 & 216.000 & 0.711 & PASM \\ 
  simple QBM vs. climate QBM & rho & t & 0.631 & 215.000 & 0.264 & PASM \\ 
  simple QBM vs. climate QBM & MAE & t & 4.276 & 216.000 & 0.000 & PASM \\ 
  simple IPM vs. climate IPM & rho & t & -1.479 & 195.000 & 0.930 & POSE \\ 
  simple IPM vs. climate IPM & MAE & t & -2.185 & 196.000 & 0.985 & POSE \\ 
  simple QBM vs. climate QBM & rho & t & -1.564 & 195.000 & 0.940 & POSE \\ 
  simple QBM vs. climate QBM & MAE & t & -2.468 & 196.000 & 0.993 & POSE \\
   \hline
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{table}[ht]
\centering
\caption {Statistical tests of model comparisons. Table shows results from one-sided t-tests for the particular comparison.}
\begin{footnotesize}
\begin{tabular}{lllrrrl}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species \\ 
  \hline
limate IPM vs. simple IPM & rho & t & 1.196 & 279.000 & 0.116 & BOGR \\ 
  climate IPM vs. simple IPM & MAE & t & -2.333 & 280.000 & 0.010 & BOGR \\ 
  climate QBM vs. simple QBM & rho & t & 1.798 & 279.000 & 0.037 & BOGR \\ 
  climate QBM vs. simple QBM & MAE & t & -3.340 & 280.000 & 0.000 & BOGR \\ 
  simple IPM vs. simple QBM & rho & t & -1.757 & 279.000 & 0.960 & BOGR \\ 
  simple IPM vs. simple QBM & MAE & t & 2.338 & 280.000 & 0.990 & BOGR \\ 
  climate IPM vs. climate QBM & rho & t & -1.083 & 279.000 & 0.860 & BOGR \\ 
  climate IPM vs. climate QBM & MAE & t & 1.151 & 280.000 & 0.875 & BOGR \\ 
  climate IPM vs. simple IPM & rho & t & 0.037 & 169.000 & 0.485 & HECO \\ 
  climate IPM vs. simple IPM & MAE & t & -2.130 & 170.000 & 0.017 & HECO \\ 
  climate QBM vs. simple QBM & rho & t & -0.747 & 169.000 & 0.772 & HECO \\ 
  climate QBM vs. simple QBM & MAE & t & 1.145 & 170.000 & 0.873 & HECO \\ 
  simple IPM vs. simple QBM & rho & t & -1.638 & 169.000 & 0.948 & HECO \\ 
  simple IPM vs. simple QBM & MAE & t & 4.011 & 170.000 & 1.000 & HECO \\ 
  climate IPM vs. climate QBM & rho & t & -0.704 & 169.000 & 0.759 & HECO \\ 
  climate IPM vs. climate QBM & MAE & t & 0.329 & 170.000 & 0.629 & HECO \\ 
  climate IPM vs. simple IPM & rho & t & -0.097 & 215.000 & 0.538 & PASM \\ 
  climate IPM vs. simple IPM & MAE & t & -0.556 & 216.000 & 0.289 & PASM \\ 
  climate QBM vs. simple QBM & rho & t & -0.631 & 215.000 & 0.736 & PASM \\ 
  climate QBM vs. simple QBM & MAE & t & 4.276 & 216.000 & 1.000 & PASM \\ 
  simple IPM vs. simple QBM & rho & t & 0.552 & 215.000 & 0.291 & PASM \\ 
  simple IPM vs. simple QBM & MAE & t & -1.033 & 216.000 & 0.151 & PASM \\ 
  climate IPM vs. climate QBM & rho & t & 2.022 & 215.000 & 0.022 & PASM \\ 
  climate IPM vs. climate QBM & MAE & t & -5.309 & 216.000 & 0.000 & PASM \\ 
  climate IPM vs. simple IPM & rho & t & 1.479 & 195.000 & 0.070 & POSE \\ 
  climate IPM vs. simple IPM & MAE & t & -2.185 & 196.000 & 0.015 & POSE \\ 
  climate QBM vs. simple QBM & rho & t & 1.564 & 195.000 & 0.060 & POSE \\ 
  climate QBM vs. simple QBM & MAE & t & -2.468 & 196.000 & 0.007 & POSE \\ 
  simple IPM vs. simple QBM & rho & t & 0.297 & 195.000 & 0.383 & POSE \\ 
  simple IPM vs. simple QBM & MAE & t & 1.027 & 196.000 & 0.847 & POSE \\ 
  climate IPM vs. climate QBM & rho & t & 1.137 & 195.000 & 0.128 & POSE \\ 
  climate IPM vs. climate QBM & MAE & t & 0.455 & 196.000 & 0.675 & POSE \\ 
   \hline
\end{tabular}
\end{footnotesize}
\end{table}

\begin{table}[ht]
\centering
\caption {Statistical tests of model comparisons at different forecast horizons. Table shows results from one-sided t-tests for the particular comparison.}
\begin{scriptsize}
\begin{tabular}{lllrrrlr}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species & horizon \\ 
  \hline
climate IPM vs. climate QBM & rho & t & -0.122 & 167.000 & 0.549 & PASM & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.394 & 149.000 & 0.347 & POSE & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.436 & 129.000 & 0.668 & HECO & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.318 & 129.000 & 0.625 & BOGR & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & -1.015 & 150.000 & 0.844 & PASM & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.876 & 132.000 & 0.809 & POSE & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.790 & 115.000 & 0.784 & HECO & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.049 & 114.000 & 0.519 & BOGR & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.610 & 129.000 & 0.272 & PASM & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.719 & 112.000 & 0.763 & POSE & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & -1.871 & 98.000 & 0.968 & HECO & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.006 & 96.000 & 0.503 & BOGR & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.761 & 108.000 & 0.224 & PASM & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.168 & 94.000 & 0.566 & POSE & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.600 & 82.000 & 0.725 & HECO & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.196 & 78.000 & 0.423 & BOGR & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.226 & 91.000 & 0.411 & PASM & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.043 & 79.000 & 0.517 & POSE & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.794 & 70.000 & 0.785 & HECO & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.180 & 65.000 & 0.429 & BOGR & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.331 & 75.000 & 0.629 & PASM & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.743 & 66.000 & 0.230 & POSE & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.658 & 59.000 & 0.743 & HECO & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.015 & 54.000 & 0.506 & BOGR & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.805 & 62.000 & 0.212 & PASM & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.222 & 53.000 & 0.587 & POSE & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -1.009 & 50.000 & 0.841 & HECO & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.095 & 44.000 & 0.537 & BOGR & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.001 & 54.000 & 0.500 & PASM & 8.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.155 & 47.000 & 0.561 & POSE & 8.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.460 & 43.000 & 0.676 & HECO & 8.000 \\ 
  climate IPM vs. climate QBM & rho & t & -1.671 & 37.000 & 0.948 & BOGR & 8.000 \\  
   \hline
\end{tabular}
\end{scriptsize}
\end{table}

\begin{table}[ht]
\centering
\caption {Statistical tests of model comparisons at different forecast horizons. Table shows results from one-sided t-tests for the particular comparison. Note the reverse order of comparisons relative to Table S23.}
\begin{scriptsize}
\begin{tabular}{lllrrrlr}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species & horizon \\ 
  \hline
climate QBM vs. climate IPM & rho & t & 0.122 & 167.000 & 0.451 & PASM & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.394 & 149.000 & 0.653 & POSE & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.436 & 129.000 & 0.332 & HECO & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.318 & 129.000 & 0.375 & BOGR & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & 1.015 & 150.000 & 0.156 & PASM & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.876 & 132.000 & 0.191 & POSE & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.790 & 115.000 & 0.216 & HECO & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.049 & 114.000 & 0.481 & BOGR & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.610 & 129.000 & 0.728 & PASM & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.719 & 112.000 & 0.237 & POSE & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & 1.871 & 98.000 & 0.032 & HECO & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.006 & 96.000 & 0.497 & BOGR & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.761 & 108.000 & 0.776 & PASM & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.168 & 94.000 & 0.434 & POSE & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.600 & 82.000 & 0.275 & HECO & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.196 & 78.000 & 0.577 & BOGR & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.226 & 91.000 & 0.589 & PASM & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.043 & 79.000 & 0.483 & POSE & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.794 & 70.000 & 0.215 & HECO & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.180 & 65.000 & 0.571 & BOGR & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.331 & 75.000 & 0.371 & PASM & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.743 & 66.000 & 0.770 & POSE & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.658 & 59.000 & 0.257 & HECO & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.015 & 54.000 & 0.494 & BOGR & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.805 & 62.000 & 0.788 & PASM & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.222 & 53.000 & 0.413 & POSE & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 1.009 & 50.000 & 0.159 & HECO & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.095 & 44.000 & 0.463 & BOGR & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.001 & 54.000 & 0.500 & PASM & 8.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.155 & 47.000 & 0.439 & POSE & 8.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.460 & 43.000 & 0.324 & HECO & 8.000 \\ 
  climate QBM vs. climate IPM & rho & t & 1.671 & 37.000 & 0.052 & BOGR & 8.000 \\ 
   \hline
\end{tabular}
\end{scriptsize}
\end{table}
